Next Trippy Structures\thanks{Supported by organization x.}

### 2019-01-07 paper.tex
Restructured

Review whatever we may have missed from state of the art in prev. papers \cite{koide2018cinct} and \cite{ding2018ultraman}. For vehicles we also have this \cite{cai2018vector} and \cite{lovell2018lossless}. On contrast, in \cite{al2017semantictraj} we have a very nice example of a text-based trajectory indexing. I need to figure out what the Geodabs thing \cite{chapuis2018geodabs} is all about.

Cite Adrian and all that crap. Also send an email to Andrea asking about \cite{rivera2018faster}; I couldn't read it yet as it's paywalled and not available on sci-hub yet!\marginnote{Contact Andrea and Diego!}

@@

\section{Proposed Structures}
\subsection{Common Structures}
We represent the network like this:

>>>>

Review whatever we may have missed from state of the art in prev. papers \cite{koide2018cinct} and \cite{ding2018ultraman}. For vehicles we also have this \cite{cai2018vector} and \cite{lovell2018lossless}. On contrast, in \cite{al2017semantictraj} we have a very nice example of a text-based trajectory indexing. Geodabs is another example of a text-based index that takes the sequence into account using fingerprinting \cite{chapuis2018geodabs}.

Apart from \cite{koide2018cinct}, in compact data structures there is PAPER ADRIAN\marginnote{We should wait to see if the Journal gets published soon}, which focuses on intersection queries for trajectories in free space, and  \cite{rivera2018faster}, which introduces two bitvectors to efficiently answer time interval queries.

@@

\section{Relevant queries}
\label{seq:rq}
We are interested in solving two kinds of queries:

\begin{enumerate}[A)]
    \item Aggregation of passengers
    \item Movement patterns
\end{enumerate}

\section{Proposed Structures}
As of today, we are not aware of any indexing structure that would allow to efficiently represent trajectories that could also support all the kinds of queries described in Section~\ref{seq:rq}. For this reason, we propose two data structures, \acumm and \ctr. The first is targeted for queries of type A, solving most aggregation queries in constant time, while the later can be used for queries of type B.

\subsection{Common Structures}
Both \acumm and \ctr need a network representation to be operated, which is represented in the following components:
